\vspace{-2cm} Government Websites As Data: \\ A methodological pipeline with application to the websites of municipalities in the United States

### 2021-06-01 paper/jitp_rr_memo/jitp_rr_memo.tex
upadted memo
revised memo to address data scope

Thank you for your comments and for giving us the opportunity to revise and resubmit our paper Thanks also to the reviewers for their constructive comments. As we hope you will see both in the revised manuscript and in this response letter, we have taken each comment seriously and have endeavored to address each as completely as possible. Each of the comments from reviewers is addressed in the order presented in the review. We do believe that addressing reviewers' comments has significantly improved the paper. We should note that we are approximately 450 words over the 5,000 limit for Workbench Notes. We thoroughly trimmed the text to make room for the revisions requested by the reviewers, but would be happy to cut or move additional content to the online appendix if we need to be under the 5,000 limit. \\

@@

	\textbf{Response}: We will make three categories of online materials available to help readers/users effectively apply the methods workflow we develop. First, we will post a conventional replication archive to Dataverse. The replication archive will include all of our code and data. Second, the \texttt{gov2text} package is available on GitHub. Third, we have posted an interactive tutorial on Google Colab that demonstrates the key steps in the application of our pipeline using the \texttt{gov2text} package.

>>>>

Thank you for your comments and for giving us the opportunity to revise and resubmit our paper Thanks also to the reviewers for their constructive comments. As we hope you will see both in the revised manuscript and in this response letter, we have taken each comment seriously and have endeavored to address each as completely as possible. Each of the comments from reviewers is addressed in the order presented in the review. We do believe that addressing reviewers' comments has significantly improved the paper. \\

@@

	\textbf{Response}: We will make three categories of online materials available to help readers/users effectively apply the methods workflow we develop. First, we will post a conventional replication archive to Dataverse. The replication archive will include all of the code necessary to replicate the text analysis results we present, as well as the raw text corpora that we extracted from the websites. Second, the \texttt{gov2text} package is available on GitHub. Third, we have posted an interactive tutorial on Google Colab that demonstrates the key steps in the application of our pipeline using the \texttt{gov2text} package.

### 2021-06-01 paper/manuscript_jitp_rr.tex
revised memo to address data scope

\vspace{-.2cm}
\section{The Web to Text Pipeline} \vspace{-.2cm}
In this section, we describe our methodological pipeline, with which we take an archive of website files, and output a corpus of formatted plain text documents. We address three methodological challenges.  First, though they contain significant amounts of text, websites are not comprised of clean plain text files. Rather, the files available at websites are of multiple types, including HTML, PDF, word processor, plain text, and image files. The first step is aimed at extracting clean plain text from this heterogeneous file base. The second step in our pipeline is to process the text to remove language that is effective at differentiating one website from another but is substantively uninformative. Finally, these tools need to work consistently across all of the websites in our corpus, in spite of the fact that relevant information is stored and structured in different ways. We make a software recommendation for each of these steps and gather most of them in our R package, \texttt{gov2text}. Some of the steps we take in this processing pipeline are universally applicable in the analysis of textual data, and some of them are most appropriate for the particular type of text analysis that we apply to this data---statistical topic modeling. We will clarify this distinction as we describe steps in our pipeline.

>>>>

\vspace{-.2cm}
\section{The Web-to-Text Pipeline} \vspace{-.2cm}
In this section, we describe our methodological pipeline, with which we take an archive of website files, and output a corpus of formatted plain text documents. We address three methodological challenges.  First, though they contain significant amounts of text, websites are not comprised of clean plain text files. Rather, the files available at websites are of multiple types, including HTML, PDF, word processor, plain text, and image files. The first step is aimed at extracting clean plain text from this heterogeneous file base. The second step in our pipeline is to process the text to remove language that is effective at differentiating one website from another but is substantively uninformative. Finally, these tools need to work consistently across all of the websites in our corpus, in spite of the fact that relevant information is stored and structured in different ways. We make a software recommendation for each of these steps and gather most of them in our R package, \texttt{gov2text}. Some of the steps we take in this processing pipeline are universally applicable in the analysis of textual data, and some of them are most appropriate for the particular type of text analysis that we apply to this data---statistical topic modeling. We will clarify this distinction as we describe steps in our pipeline.
